Selective electroporation of the viral envelope

### 2021-04-08 documents/pure_electroporation.tex
Convolution working properly

@@

ultracrepidarian

@@

Kotnik note an important fact: all these permittivity and conductivity values will also depend on frequency, which is not included in their model. We have not examined how these factors can be extracted from

@@

Kotnik-simulchouski

(Helmholz)

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing.

Lagrange multipliers. Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin),

The impulse response is the derivative of the step response. The convolution integral (or sum, in the discrete case) can be performed

>>>>

In a continued effort to which make ultracrepidarian physicist such as ourselves feel useful indirectly biological

@@

@@

Kotnik note an important fact: all these permittivity and conductivity values will also depend on frequency, which is not included in their model. We have not examined how these factors can be extracted from. Also disregarded are the Poisson-boltzmann shielding space-charges that proved all-important in the last study.

@@

Several groups have discussed optimizing

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control.

Lagrange multipliers. Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin or when permittivity is neglected) [schwan paper],

Kotnik discuss the transmembrane voltage due to several pulse shapes formed from the Laplace Transform of the original differential equation. Talele offer their own response due to an arbitrary waveform can be produced by

The impulse response is the derivative of the step response. The convolution integral (or sum, in the discrete case) can be performed either with the derivative of the input function and the step response, or the impulse response and the input function as algebraic convenience demands. Unfortunately

There exists an alternative convolution technique, due to the Convolution Property of the fourier transform.

The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size.
